A Roadmap for\\HEP Software and Computing R\&D\\for the 2020s

### 2018-11-06 CWP/papers/HSF-CWP-2017-01_roadmap/latex/cwp-main.tex
Avoid unwarrented assertion about other fields' development practice

Unlike the situation that is traditional in some other fields, in
which users express their requirements and computer specialists
implement solutions, there is a close collaboration, even overlap,
in HEP between users and developers that is essential for our success.
Many details of experiment data
cannot be known before data taking has started, and each change in
detector technology or machine performance improvement can have
important consequences for the software and computing infrastructure. In
the case of detectors, engineers and physicists are required to have a
good understanding of each other's field of expertise. In the same way,
it is necessary that physicists understand some of the complexities of
writing software, and that software experts are able to fathom the
requirements of physics problems.

>>>>

There is a very close collaboration, even overlap,
in HEP between users of software and developers. This has given experiments
an agility that was often essential for success in the past.
Many details of experiment data
cannot be known before data taking has started, and each change in
detector technology or machine performance improvement can have
important consequences for the software and computing infrastructure. In
the case of detectors, engineers and physicists are required to have a
good understanding of each other's field of expertise. In the same way,
it is necessary that physicists understand some of the complexities of
writing software, and that software experts are able to fathom the
requirements of physics problems.
